---
title: "p8105_hw1_LC4052"
author: "Linqi Chu"
output: html_document
date: "2025-09-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(moderndive)
library(tidyverse)

```

## Problem 1

1. Load the dataset.

```{r}
data("early_january_weather")

```

2. Describe the data.

```{r}
# Names and values of important variables
str(early_january_weather)
early_january_weather = janitor::clean_names(early_january_weather)
names(early_january_weather)

```

```{r}
# size of the dataset
nrow(early_january_weather)
ncol(early_january_weather)

```

```{r}
# The mean temperature
mean_tmp = mean(early_january_weather$temp)
mean_tmp

```

The variables in this dataset include "origin", "year", "month", "day", "hour", "temp", "dewp", "humid", "wind_dir" ,"wind_speed", "wind_gust", "precip", "pressure", "visib", and "time_hour".

The dataset has 358 rows and 15 columns. The mean temperature is 39.58212.


```{r}
# Make a scatterplot of temp (y) vs time_hour (x)
weather_scatterplot = ggplot(data = early_january_weather, 
  mapping = aes(x = time_hour, y = temp, color = humid))+ 
  geom_point(alpha = 0.7) + 
  labs(
    title = "Temperature vs. Time_hour",
    x = "Time Hour",
    y = "Temperature (°F)",
    color = "Humidity (%)") +
  scale_x_datetime(
    date_breaks = "2 days",
    date_labels = "%b %d"
  )
  
weather_scatterplot

```

There is a general upward trend in temperature as time progresses from Jan 02 towards Jan 14. 

Within each day, temperature shows a cyclical pattern. It tends to be low during the early hours, becomes higher later and turns lower at the end of the day.

There is a correlation between temperature and humidity. Points with higher humidity are mostly concentrated in areas with lower temperatures, while points with lower humidity are more likely to be found in regions with higher temperatures.

There is some variability in the data. For example, from Jan 12 to Jan 14, there are points with relatively high temperatures, and the humidity values are also high.


```{r}
# Export the scatterplot
ggsave(
  "weather_temp_time_scatterplot.png",
  plot = weather_scatterplot,
  width = 10, 
  height = 6, 
  dpi = 300
)

```




## Problem 2

```{r}
# Create a dataframe

df = tibble(
  # a random sample of size 10 from a standard Normal distribution
  norm_sample = rnorm(n = 10, mean = 0, sd = 1),  
  # a logical vector indicating whether elements of the sample are greater than 0
  log_vec = norm_sample > 0,  
  # a character vector of length 10
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  # a factor vector of length 10, with 3 different factor “levels”
  factor_vec = factor(c("low", "low", "mid", "mid", "mid", "high", "high", "high", "low", "mid"), levels = c("low", "mid", "high"))  
)

df


```

### Calculate mean

```{r}
nd = pull(df, norm_sample)
log_vec = pull(df, log_vec)
char_vec = pull(df, char_vec)
factor_vec = pull(df, factor_vec)

```

```{r}
mean_nd = mean(nd)
mean_nd

```

```{r}
mean_log = mean(log_vec)
mean_log

```

```{r}
mean_char = mean(char_vec)
mean_char

```

```{r}
mean_factor = mean(factor_vec)
mean_factor

```

We can take the mean of random sample and logical vector. The character vector and factor vector do not work.


```{r eval = FALSE}
as.numeric(df$log_vec)
as.numeric(df$char_vec)
as.numeric(df$factor_vec)

```









